A protocol and event-sourced database for decentralized user-siloed data

### 2019-09-27 draft.tex
updates
Signed-off-by: andrew <andrew@textile.io>

\title[An event-sourced and decentralized database with IPLD and materialized views]{An event-sourced and decentralized database with IPLD and materialized views}
\author{Pick}
\author{Farmer}
\author{Sutula}
\author{Hill}
\affiliation{www.textile.io} \email{contact@textile.io}

@@

A view Model is generally defined by custom update logic (i.e., a Reducer), a (possibly ORM\footnote{Object-relational mapping}-based) view Store for persistence, an Event Bus (or Broadcaster) for notifying downstream consumers, and a set of query/\emph{Resolver} \cite{ereminReduxInspiredBackend2019} functions. In practice, a view Model may \emph{also} wrap the Event Creator application logic that is used to generate upstream Events. This provides an intuitive, singular access point to the \emph{local} system, while also leaving room for updates via \emph{external} peer-events.

@@

\appendix

% [!p] forces it to just take the whole page
\begin{example*}[!p]
\section{Event node interface} \label{appx:EventNode} % stuck it inside the example so it lands on the same full page
\begin{lstlisting}
// Node is the most basic component of a log.
// Note: In practice, this is encrypted with the Follow Key.
type Node interface {
    ipld.Node

@@

>>>>

\title[A protocol and event-sourced database for decentralized user-siloed data]{A protocol and event-sourced database for decentralized user-siloed data}
\author{Pick}
\author{Farmer}
\author{Sutula}
\affiliation{www.textile.io} \email{research@textile.io}
\author{?Others?}
\affiliation{other?} \email{research@textile.io}
\author{Hill}
\affiliation{www.textile.io} \email{contact@textile.io}

@@

A view Model is generally defined by custom update logic (i.e., a Reducer), a (possibly ORM\footnote{Object-relational mapping}-based) view Store for persistence, an Event Bus (or Broadcaster) for notifying downstream consumers, and a set of query/\emph{Resolver} \cite{ereminReduxInspiredBackend2019} functions. In practice, a view Model may \emph{also} wrap the Event Creator application logic that is used to generate upstream Events. This provides an intuitive, singular access point to the \emph{local} system, while also leaving room for updates via \emph{external} peer-events. In practice, the Store is a lightweight interface that can be implemented by one of many database management systems (\ref{appx:DBMS}).

@@

\appendix 
% [!p] forces it to just take the whole page
\begin{example*}[!p]
\section{Event node interface} \label{appx:EventNode} % stuck it inside the example so it lands on the same full page
\begin{lstlisting}
// Node is the most basic component of a log.
// Note: In practice, this is encrypted with the Follow Key.
type Node interface {
    ipld.Node

@@

\onecolumn
\section{Database Management Systems (DBMS)} \label{appx:DBMS}

\begin{enumerate}
	\item Relational
    \begin{enumerate}
        \item MariaDB \url{https://mariadb.org/}
    	\item PostgreSQL \url{https://www.postgresql.org/}
        \item SQLite \url{https://www.sqlite.org}
    \end{enumerate}
    \item Key value stores
    \begin{enumerate}
        \item Dynamo \url{https://aws.amazon.com/dynamodb/}
    	\item LevelDB \url{https://github.com/google/leveldb}
        \item Redis \url{https://redis.io/}
    \end{enumerate}
    \item Document stores
    \begin{enumerate}
        \item CouchDB \url{http://couchdb.apache.org/}
    	\item MongoDB \url{https://www.mongodb.com/}
        \item RethinkDB \url{https://rethinkdb.com/}
    \end{enumerate}
\end{enumerate}
